\documentclass{article}
% !TEX root
\usepackage[a4paper, margin=0.5in]{geometry}
% \usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{graphicx}
% \usepackage{enumitem}
\usepackage{enumerate}
\usepackage{tikz}
\usepackage{array}
\usepackage{listings}
\usepackage{color}
\usepackage{upquote}
% \usepackage{wasysym}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{pgfplots}
\usepackage{diagbox}
\usepackage{subfiles}

\setlength{\columnsep}{1cm}

\pgfplotsset{compat=1.14}
\usepackage{macros} 

\graphicspath{ {images/} }

\title{CPSC 418 Review}

\author{
    \begin{tabular}{lll}
        Zhenpeng Wu & 28125152 & w8j0b\\
    \end{tabular}
}

\begin{document}

% \maketitle

\section{Erlang}

\subfile{"sections/01. Erlang"}

\pagebreak

\section{Reduce}

\subfile{"sections/02. Reduce"}

\section{Scan}

\subfile{"sections/03. Scan"}

\pagebreak

\section{Shared Memory Multiprocessors - Parallel Models}

\subfile{"sections/04. Shared Memory Multiprocessors"}

\pagebreak

\section{Message Passing Computers - Parallel Models}

\subfile{"sections/05. Message Passing Computers"}

\pagebreak

\section{Superscalar Processors: Computer Architecture - Parallel Models}

\subfile{"sections/06. Superscalar Processors"}

\pagebreak

\section{Comparisons among Shared Memory, Message Passing, and Superscalar}

\subfile{"sections/07. Compare Models"}

\pagebreak

\section{Parallel Performance, Speedup and Efficiency}

\subfile{"sections/08. Parallel Performance, Speedup and Efficiency"}

\pagebreak

\section{Performance Loss}

\subfile{"sections/09. Performance Loss"}

% \pagebreak

\section{Models of Parallel Computation}

\subfile{"sections/10. Models of Parallel Computation"}

% \pagebreak

\section{Energy and Parallel Computing}

\subfile{"sections/11. Energy and Parallel Computing"}

\pagebreak

\section{Sorting Networks}

\subfile{"sections/12. Sorting Networks"}

\pagebreak

\section{Data Parallel Computing and CUDA}

\subfile{"sections/13. Data Parallel Computing and CUDA"}

\appendix

\end{document}
